Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 introduction.tex
edits to the intro to tighten languange and save some space

Many websites and apps are designed to facilitate joint discovery,
sharing, and recommendations of content.
Such sites include news, photo, and video sharing sites,
sites to review restaurants, hotels, or travel experiences,
online stores at which users write reviews (such as Amazon),
and citizen science projects
(such as eBird \citep{sullivan2009ebird,xue-ebird} or Galaxy Zoo \citep{lintott-galaxy-zoo}).
By learning from the experiences of other users, individuals can
improve their own experience \citep{schmit2017human}.

Viewed more abstractly, users jointly explore a space of
many options (products, news stories, photos, birdwatching sites,
patches of sky to train their telescopes on, $\ldots$),
with the implicit goal of identifying the ``best'' ones.
Therefore, such scenarios can be fruitfully modeled in a bandit
learning framework.
However, contrary to standard bandit settings, the utilities of the
decision makers (the users) are not aligned with the overall utility.
Societally (i.e., in a suitable aggregate over all users),
it would be desirable to engage in considerable exploration of
different options, so as to provide higher rewards for a large number
of future users.
However, individual users only interact with the site a limited number
of times, and therefore have little incentive for exploration.
A particularly clean model is obtained when each user interacts with the
site only once, and hence has no intrinsic utility for exploration. 
This model has been the subject of prior work, and forms the basis of
the present submission.

To effect an outcome close to societally optimal,
it is necessary to provide exploration incentives to the individual users.
This was noted in two recent lines of work:
\citet{kremer2014implementing}
and
\citet{mansour2015bayesian,mansour2016bayesian,mansour2018competition}
(see \cite{slivkins:asymmetry} for a high-level overview)
assume that the site (also called the \emph{principal}) has an
informational advantage in being the only one to observe the results
of past arm pulls.
(Such an assumption applies, for instance, to route recommendations in
driving.)
The principal can exploit her%
\footnote{We use male pronouns to refer to users and female pronouns
  to refer to the principal.}
advantage and make recommendations to the individual agents that 
are in their best interest to follow.
\citet{frazier2014incentivizing} and 
\citet{han2015incentivizing} instead assume that the results of all
past arm pulls are publicly observable
(such as reviews on an online retail site).
They instead suppose that the principal can offer payments to users as
a reward for pulling particular arms.
We follow the model of \citet{frazier2014incentivizing} and
\citet{han2015incentivizing} 
and consider a multi-armed bandit model in which the principal can
offer payments to the users for pulling particular arms.

Past work has assumed that users are homogeneous, i.e., the expected
reward a user derives from an arm is the same for all users.%
\footnote{\citet{han2015incentivizing} assume that users are
heterogeneous in their tradeoff between utility derived from arm pulls
and utility derived from the principal's payment.}
In reality, users have different preferences, e.g., gastronomic,
political, aesthetic, practical, etc.
Indeed, the websites and mobile apps most widely used for joint discovery,
sharing, and recommendation of content tend to concern products and items 
with large amounts of heterogeneity in preferences (movies, restaurants,
videos, travel experiences), and not items which have a universally
agreed-on best order.
This is perhaps because regimes with heterogeneous preferences are the
ones where discovery of the best items is the most difficult for people, 
and thus where online
platforms tend to provide the greatest value.  Thus, we see an appropriate
accounting for heterogeneity as critical to an understanding of incentivizing
exploration in online communities.

>>>>

Many websites and apps facilitate joint discovery,
sharing, and recommendation of content.
This includes news-, photo-, and video-sharing sites;
sites that host user-written reviews of products, restaurants, hotels, and travel experiences;
and citizen science projects
such as eBird \citep{sullivan2009ebird,xue-ebird} and Galaxy Zoo \citep{lintott-galaxy-zoo}.
Users of these sites improve their own experiences 
by learning from the experiences of others 
\citep{schmit2017human}.

Viewed more abstractly, users jointly explore a space of
options (products, news stories, photos, birdwatching sites,
%patches of sky to train their telescopes on, 
$\ldots$),
with the implicit goal of identifying the ``best'' ones.
Such scenarios are often modeled in a bandit
learning framework.
However, unlike standard bandit settings, the utilities of the
decision makers (the users) are not aligned with overall utility.
Societally (i.e., in a suitable aggregate over users),
substantial exploration of options could provide higher future rewards.
However, individual users interact with the site a limited number
of times, and therefore have little incentive to explore.
Recent work has focused on the setting where users interact only once, 
and so have no intrinsic incentive to explore.

Two recent lines of work have shown that
effecting a societally near-optimal outcome in this setting requires
explicitly incentivizing exploration:
\citet{kremer2014implementing}
and
\citet{mansour2015bayesian,mansour2016bayesian,mansour2018competition}
(see \cite{slivkins:asymmetry} for an overview)
assume that the site (also called the \emph{principal}) has an
informational advantage in being the only one to observe the results
of past arm pulls
(as in driving route recommendations).
The principal can use her%
\footnote{We use male pronouns to refer to users and female pronouns
  to refer to the principal.}
advantage to induce exploration by recommending apparently sub-optimal arms,
as long as agents cannot do better on their own.
\citet{frazier2014incentivizing} and 
\citet{han2015incentivizing} instead assume that the results of all
past arm pulls are publicly observable
(as on a review-sharing site).
They suppose the principal can incentivize exploration by offering payments to users as
a reward for pulling particular arms.
We follow this second model.
% We follow the model of \citet{frazier2014incentivizing} and
% \citet{han2015incentivizing} 
% and consider a multi-armed bandit model in which the principal can
% offer payments to the users for pulling particular arms.

Past work has assumed that users are homogeneous, i.e., the expected
reward derived from an arm is the same for all users.%
\footnote{\citet{han2015incentivizing} assume that users are
heterogeneous in their tradeoff between utility derived from arm pulls
and utility derived from the principal's payment.}
In reality, users have different preferences, e.g., gastronomic,
political, aesthetic, practical.
Indeed, the websites and mobile apps most widely used for joint discovery,
sharing, and recommendation of content tend to concern products and items 
with heterogeneity in preferences (movies, restaurants,
videos, travel experiences), and not items which have a universally
agreed-on best order.
This is perhaps because regimes with heterogeneous preferences are the
ones where discovery of the best items is the most difficult for people, 
and thus where online
platforms provide the most value.  Thus, we see an appropriate
accounting for heterogeneity as critical to an understanding of incentivizing
exploration in online communities.
